### 2025-01-08 paper/icml25/first/sects/introduction.tex
added evaluation (WIP)
chore: try to clarify sample inefficient part

\section{Introduction}

Learnign control policies has important applications in robotics~\cite{Singh22}, autonomous driving~\cite{Elallid22}, swarm intelligence~\cite{Tang21} and many other fields. These scenarios presents a variaty of different challenges, such as sparse rewards, complex dynamics, and multi-agent interactions. Current approaches often focus on either single- or multi-agent scenarios, lacking a unified solution that works effectively in both settings. Moreover, reinforcement learning algorithms tend to be sample inefficient due to the high variance of the gradient estimates and the exploration required \texttt{\color{DarkOrchid}{<- FB: non mi è super chiara questa frase}}. A recently introduced method for the latter problem is SHAC~\cite{Xu22} which exploits differentiable simulators to provide precise gradient information, thereby expediting policy optimization and improving learning efficiency.

>>>>

\section{Introduction}\label{sect:introduction}

Learning control policies has important applications in robotics~\cite{Singh22}, autonomous driving~\cite{Elallid22}, swarm intelligence~\cite{Tang21} and many other fields. These scenarios present a variety of different challenges, such as sparse rewards, complex dynamics, and multi-agent interactions. Current approaches often focus on either single- or multi-agent scenarios, lacking a unified solution that works effectively in both settings. Moreover, reinforcement learning algorithms tend to be \emph{sample inefficient}, namely requiring a large number of interactions with the environment to learn a good policy.
\texttt{\color{DarkOrchid}{<- FB: non mi è super chiara questa frase}}. A recently introduced method for the latter problem is SHAC~\cite{Xu22} which exploits differentiable simulators to provide precise gradient information, thereby expediting policy optimization and improving learning efficiency.
